### 2023-10-18 vesicle_code/docs/confinedMulti/response.tex

The referee wrote: The authors study the passage of a vesicle through a
constriction. A vesicle’s membrane has some mechanical properties analog
to red blood cells motivating many theoretical and numerical studies.
Indeed, this issue has known many progress during the last decade. A
vesicle is also a fascinating physical soft particle as its membrane
area is constant as well as its volume leading to an essential role of
deflation. But contrary to capsules, as the membrane is fluid, there is
no buckling. Finally, the study is inspired by modeling RBC.

\noindent
{\bf Response:} We thank the referee for their assessment and suggested
changes.

\begin{enumerate}
%%%%%%%%
\item This study is limited to the two-dimensional case, which is not
  reality. It is a strong approximation and full 3D studies are still a
    challenge in constrictions. But, in the axisymmetrical case, there
    are several results in literature which could be more or less,
    considered as benchmark:
    \url{http://dx.doi.org/10.1103/PhysRevFluids.5.043602}, \\
    \url{https://doi.org/10.1017/jfm.2017.743}

\noindent
{\bf Response:} Thank you for the comment. It is addressed in detail in
our response to the reviewer's second comment.

@@

%%%%%%%%
\item The authors should justify why they limit their investigations to
  the 2D case if 3D is possible. I note that the authors also cite
    relevant literature as 10, 11 $\ldots$ References to 2D are
    excellent. A typical argument is the high time of 3D simulations.
    Can the authors provide an order of magnitude?

\noindent
{\bf Response:} There is published work that has investigated elements
of our work in  3D. This includes the papers from the reviewers first
comment that consider vesicles in strong confinement, but these works
assume axisymmetry and neither consider multicomponent vesicles. Two
3D works that relax the axisymmetric assumption and simulate vesicles in
strong confinement are also cited in the original submission
(https://doi.org/10.1063/1.5081057 and
https://doi.org/10.1103/PhysRevFluids.5.013603). Red blood cells
undergoing strong confinement has also been considered using other
numerical methods including a spring model coupled to smoothed particle
hydrodynamics (http://dx.doi.org/10.1016/j.taml.2015.11.006 and
http://dx.doi.org/10.1063/1.4817959). These papers are cited in the
revised manuscript.

There is much less work on 3D multicomponent vesicles. Phase field
models are used by Wang and Du
(https://doi.org/10.1007/s00285-007-0118-2) and a level set method is
used by Gera and Salac
(https://doi.org/10.1016/j.compfluid.2018.04.003). The challenge with
both these approaches is that they have to discretize the fluid volume,
and this limits how small $\epsilon$ can be, and therefore restricts
the sharpness of the transition between the floppy and stiff
regions. In both these works, a value of $\epsilon$ that is at least
ten-times larger than the more realistic value used in our work. To use
a comparable value to ours, they would have to increase the overall
spatial resolution by $10^3$. These codes are parallelized and highly
optimized, but they still take on the order of a day to complete one
unconfined simulation at the coarser resolution. Therefore, with
confinement, and the additional resolution to resolve the more physical
value of $\epsilon$, a single simulation would require much more
computational resources for generating an appropriately large dataset to
analyze. For example, if a simulation for an unconfined case requires
one day of CPU time on 12 cores, then, even without confinement, the
additional resolution required to resolve the smaller value of
$\epsilon$ would require 12,000 cores to complete the simulation in the
same wall clock time, and this is assuming the code scales perfectly.
This increase in resources would be compounded further once strong
confinement is introduced.

@@

%There are 3D BIE codes for vesicles with surface rheology. Leonetti did
%in 2016 in paper Yuan is sending me. There, of course, is also plenty of
%accurate methods for single-component vesicles in 3D with strong
%confinement. This will be even more challenging with strong confinement.
%Only methods in the literature seem to be David Salac which is a
%low-order method. Can reference private discussions Zhangli Peng at UIC.
%
%A response

%%%%%%%%
\item The authors present the essential steps of the numerical model. It
  is well done and the references well chosen. I have appreciated the
    introduction of equation (9) an figure 2. However, there are two
    points to clarify :
    \begin{itemize}
      \item page 2: there is a difference in literature of the
        capillary number. Some authors use the flow curvature, others
        the mean velocity as the authors. Please explain your choice.
      \item page 2, right column ``The parameter $\epsilon \ll 1$ sets
        the size of the transition region of u, and the parameter a is
        line tension scaled by the characteristic bending stiffness. All
        simulations use the parameter values $\epsilon = 100$ and $a =
        0.04.$" $\epsilon = 100$ is contradictory to $\epsilon \ll 1$.
        Please explain or correct
    \end{itemize}

\noindent
{\bf Response:} We use the maximum imposed velocity to define the
capillary number so that we can compare our results with work that we
cite including [10,11,18] (as numbered in our original submission). We
have also added a note that the capillary number is larger for a vesicle
inside the stenosis.

For the comment regarding the value of $\epsilon$, we had a
typo. The parameter value for $\epsilon$ is actually 0.04, and this has
been fixed.

@@

%%%%%%%%
\item Why do authors never observe the blocking of vesicles contrary to
  experiments? It would the opportunity to perform a phase diagram and
    to show the effect of multicomponent.

\noindent
{\bf Response:} We initially explored cases where the single-component
vesicle became stuck, expecting that the multicomponent vesicle may pass
through the same geometry. We did not find any such cases.
However, we did observe other behaviors that differ between the two
cases, including the vesicle shape, tank treading velocity, lubrication
layer, and these comparisons are the focus of our manuscript. We defer
our response to the phase diagram point until comment number 6.

@@

%%%%%%%%
\item In experiments, the channel is a slit. What do the authors expect
  from such a difference?

\noindent
{\bf Response:} We can compare Zhangli Peng's results, our simulations
look similar to what they observe in a 2D projection of their 3D
results. They call their geometry a `slit' geometry. This work is
published, so we can reference a particular figure from the paper.

%%%%%%%%
\item Finally, this study is interesting and provides new insights.
  However, I advise authors to improve the quantitative part of their
  results (variation with Ca or confinement or something else, phase
  diagram...) to be more relevant for a journal such as Soft Matter. I
  am waiting the new manuscript.

\noindent
{\bf Response:} A phase diagram is included in Figure~\ref{fig:Phase}.
We do not observe any dependence on the capillary number. We had a
discussion with an experimental colleague who works on an experiment
with a red blood cell passing through stenosis, where only a single RBC
can pass through one at a time. His experiments have shown that the
shape of the RBC inside this confined stenosis is independent over a
range of capillary numbers, as we report in Figure~\ref{fig:Phase}. For
this reason, we do not include phase diagrams in our manuscript. We have
started examining the dependence of these dynamics on other
dimensionless parameters including the confinement ratio and the
floppy-to-stiff ratio. This will be a different focus and would distract
from the focus of this work.
\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{phaseDiagram.jpg}
  \caption{\label{fig:Phase} A phase diagram of a single vesicle in an unconfined
  nonlinear shear flow. The capillary number has no effect on the steady
  state shape of the vesicle.}
\end{figure}

### 2023-10-18 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions with Yuan

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows). The lubrication layer (gray region), defined in
  Section~\ref{sec:LL}, plays a key role in the vesicle dynamics.}
\end{figure}
We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 4 \times 10^{-6}$~m, a maximum bending stiffness
$b_{\max} = 2 \times 10^{-18}$~J, and fluid viscosity $\mu = 5 \times
10^{-2}$~kg/ms. The resulting bending relaxation time scale is $\mu
R_0^3/b_{\max} = 1.6$~s, the velocity scale is
$b_{\max}/\mu R_0^2=2.5$~$\mu$m/s, the pressure scale is $b_{\max}/R_0^3
= 3.1 \times 10^{-2}$~Pa, and the tension scale is $b_{\max}/R_0^2 = 1.3
\times 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a maximum imposed velocity, $U$, which
sets the capillary number $Ca = U R_0^{2} \mu/b_{\max}$, and $W/R_0$ is
the dimensionless width of the channel which varies in both examples we
consider. Finally, the Peclet number of the lipid dynamics is taken to
be $Pe = 1$ which results in a diffusion time scale of $6.4 \times
10^{-4}$~s. Therefore, phase separation occurs at a rate three orders of
magnitude faster than vesicle relaxation. The effect of the Peclet
number has been examined~\cite{liu-mar-li-vee-low2017,
soh-tse-li-voi-low2010}, and it has no qualitative effect on the vesicle
dynamics. From this point onwards, all equations are dimensionless.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows). The lubrication layer (gray region), defined in
  Section~\ref{sec:LL}, plays a key role in the vesicle dynamics.}
\end{figure}
We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 4 \times 10^{-6}$~m, a maximum bending stiffness
$b_{\max} = 2 \times 10^{-18}$~J, and fluid viscosity $\mu = 5 \times
10^{-2}$~kg/ms. The resulting bending relaxation time scale is $\mu
R_0^3/b_{\max} = 1.6$~s, the velocity scale is
$b_{\max}/\mu R_0^2=2.5$~$\mu$m/s, the pressure scale is $b_{\max}/R_0^3
= 3.1 \times 10^{-2}$~Pa, and the tension scale is $b_{\max}/R_0^2 = 1.3
\times 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a maximum imposed velocity, $U$, which
sets the capillary number $Ca = U R_0^{2} \mu/b_{\max}$, and $W/R_0$ is
the dimensionless width of the channel which varies in both examples we
consider. 
\textcolor{blue}{
Note that the maximum velocity inside the stenosis is almost five times
larger than the maximum imposed velocity. As a result, the capillary
number inside the stenosis is also five times larger.
}
Finally, the Peclet number of the lipid dynamics is taken to
be $Pe = 1$ which results in a diffusion time scale of $6.4 \times
10^{-4}$~s. Therefore, phase separation occurs at a rate three orders of
magnitude faster than vesicle relaxation. The effect of the Peclet
number has been examined~\cite{liu-mar-li-vee-low2017,
soh-tse-li-voi-low2010}, and it has no qualitative effect on the vesicle
dynamics. From this point onwards, all equations are dimensionless.
